---
title: "Exploratory Statistics (weighted)"
author: "Christian Hicks"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---
<a href="https://www.christianhicks.com">Return home</a> / <a href="https://www.christianhicks.com/MPH-Manuscript">Return to project</a>.
```{r setup, include=FALSE, cache=FALSE}
pacman::p_load('knitr', 'broom', 'Hmisc', 'survey', 'tidyverse')
opts_chunk$set(echo = F)
df_combined <- readRDS('data/combined.Rds')
attach(df_combined)

# Read all exploratory files
src_names <- c('chol', 'work', 'age', 'bmi', 'gender', 'race', 'edu', 'poverty',
               'doctor', 'sitting', 'phys_work', 'phys_rec')
src_files <- lapply(src_names,
                    function(x){
                      paste0('../src/exploratory/exp_', x, '.R')
                    })
lapply(src_files, knitr::read_chunk)

# Weighted data
svy1 <- svydesign(ids = SEQN,
                  weights = weight_mec,
                  data = df_combined)
```

## Main study
### Blood Cholesterol
```{r chol_plot}
```

### Working hours
```{r work_plot}
```

## Demographics
### Age
```{r age_plot}
```

### BMI
```{r bmi_plot}
```

### Gender
```{r gender_plot}
```

### Race/Ethnicity
```{r race_plot}
```

### Education
```{r edu_plot}
```

### Poverty
```{r poverty_plot}
```

Poverty is based on family size, income, and location. A value of `1` represents the poverty threshold. Ratios over `5` are categorized as `5` to preserve anonymity.

## Questionnaire
### Doctor opinion
```{r doc_plot}
```

### Sitting minutes
```{r sitting_plot}
```

### Vigorous activity at work
```{r phys_work_plot}
```

### Vigorous recreational activity
```{r phys_rec_plot}
```