---
title: "Exploratory Statistics (weighted)"
author: "Christian Hicks"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
pacman::p_load('knitr', 'broom', 'Hmisc', 'survey', 'tidyverse')
knitr::read_chunk('../src/exploratory/exp_chol.R')
knitr::read_chunk('../src/exploratory/exp_work.R')
knitr::read_chunk('../src/exploratory/exp_age.R')
knitr::read_chunk('../src/exploratory/exp_bmi.R')
knitr::read_chunk('../src/exploratory/exp_gender.R')
knitr::read_chunk('../src/exploratory/exp_race.R')
knitr::read_chunk('../src/exploratory/exp_edu.R')
knitr::read_chunk('../src/exploratory/exp_poverty.R')
knitr::read_chunk('../src/exploratory/exp_doctor.R')
knitr::read_chunk('../src/exploratory/exp_sitting.R')
knitr::read_chunk('../src/exploratory/exp_phys_work.R')
knitr::read_chunk('../src/exploratory/exp_phys_rec.R')
knitr::opts_chunk$set(echo = TRUE)
df_combined <- readRDS('./data/combined.Rds')
attach(df_combined)
svy1 <- svydesign(ids = SEQN,
                  weights = weight_mec,
                  data = df_combined)
```

## Main study
### Blood Cholesterol
```{r chol_plot, echo=FALSE}
```

### Working hours
```{r work_plot, echo=FALSE}
```

## Demographics
### Age
```{r age_plot, echo=FALSE}
```

### BMI
```{r bmi_plot, echo=FALSE}
```

### Gender
```{r gender_plot, echo=FALSE}
```

### Race/Ethnicity
```{r race_plot, echo=FALSE}
```

### Education
```{r edu_plot, echo=FALSE}
```

### Poverty
```{r poverty_plot, echo=FALSE}
```

Poverty is based on family size, income, and location. A value of `1` represents the poverty threshold. Ratios over `5` are categorized as `5` to preserve anonymity.

## Questionnaire
### Doctor opinion
```{r doc_plot, echo=FALSE}
```

### Sitting minutes
```{r sitting_plot, echo=FALSE}
```

### Vigorous activity at work
```{r phys_work_plot, echo=FALSE}
```

### Vigorous recreational activity
```{r phys_rec_plot, echo=FALSE}
```