---
title: "Bivariate Analyses with Total Blood Cholesterol"
author: "Christian Hicks"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE, cache=FALSE}
pacman::p_load('knitr', 'broom', 'survey', 'tidyverse')
knitr::read_chunk('../src/bivariate/biv_work.R')
knitr::read_chunk('../src/bivariate/biv_age.R')
knitr::read_chunk('../src/bivariate/biv_bmi.R')
knitr::read_chunk('../src/bivariate/biv_gender.R')
knitr::read_chunk('../src/bivariate/biv_race.R')
knitr::read_chunk('../src/bivariate/biv_education.R')
knitr::read_chunk('../src/bivariate/biv_poverty.R')
knitr::read_chunk('../src/bivariate/biv_doctor.R')
knitr::read_chunk('../src/bivariate/biv_sitting.R')
knitr::read_chunk('../src/bivariate/biv_phys_work.R')
knitr::read_chunk('../src/bivariate/biv_phys_rec.R')
opts_chunk$set(echo = TRUE)
df_combined <- readRDS('data/combined.Rds')
attach(df_combined)

# Factorizing variables
gender <- as.factor(gender)
chol_doctor_hi <- as.factor(chol_doctor_hi)
phys_work_vig <- as.factor(phys_work_vig)
phys_rec_vig <- as.factor(phys_rec_vig)
race_eth <- as.factor(race_eth)
education <- as.factor(education)
chol_label <- 'total cholesterol (mg/dL)'
quant <- c(0.25, 0.5, 0.75)

# Weighted data
svy1 <- svydesign(ids = df_combined$SEQN,
                  weights = df_combined$weight_mec,
                  data = df_combined)
```

## Main Study

### Working Hours
```{r wrk_reg, include=FALSE}
```

```{r wrk_hrs_output, echo=FALSE}
```

Correlation: `r c_wrk_wtd`

## Demographics

### Age
```{r age_reg, include=FALSE}
```

```{r age_output, echo=FALSE}
```

Correlation: `r c_age_wtd`

### BMI

```{r bmi_reg, include=FALSE}
```

```{r bmi_output, echo=FALSE}
```

Correlation: `r c_bmi_wtd`

### Gender
```{r gender_tt, include=FALSE}
```

```{r gender_output, echo=FALSE}
```

T test:

`r ttest_gen_wtd %>% tidy() %>% kable()`

Female mean (SD): `r mean_gen_f_wtd[1] %>% format(digits = 5)` (`r sd_gen_f_wtd %>% format(digits = 4)`)

Male mean (SD): `r mean_gen_m_wtd[1] %>% format(digits = 5)` (`r sd_gen_m_wtd %>% format(digits = 5)`)

### Race/Ethnicity
```{r race_anova, include=FALSE}
```

```{r race_output, echo=FALSE}
```

ANOVA:

`r anova_race_wtd %>% tidy() %>% kable()`

Pairwise:

`r pw_race_wtd %>% kable()`

Hispanic mean (SD): `r mean_race_1_wtd %>% format(digits = 6)` (`r sd_race_1_wtd %>% format(digits = 4)`)

Non-Hispanic White mean (SD): `r mean_race_3_wtd %>% format(digits = 5)` (`r sd_race_3_wtd %>% format(digits = 4)`)

Non-Hispanic Black mean (SD): `r mean_race_4_wtd %>% format(digits = 5)` (`r sd_race_4_wtd %>% format(digits = 5)`)

Non-Hispanic Asian mean (SD): `r mean_race_6_wtd %>% format(digits = 5)` (`r sd_race_6_wtd %>% format(digits = 4)`)

Other race or Multi-Racial mean (SD): `r mean_race_7_wtd %>% format(digits = 5)` (`r sd_race_7_wtd %>% format(digits = 4)`)

### Education
```{r education_anova, include=FALSE}
```

```{r education_output, echo=FALSE}
```

ANOVA:

`r anova_edu_wtd %>% tidy() %>% kable()`

No H.S. diploma mean (SD): `r mean_edu_1_wtd %>% format(digits = 5)` (`r sd_edu_1_wtd %>% format(digits = 4)`)

H.S. or GED mean (SD): `r mean_edu_3_wtd %>% format(digits = 5)` (`r sd_edu_3_wtd %>% format(digits = 4)`)

Some college mean (SD): `r mean_edu_4_wtd %>% format(digits = 5)` (`r sd_edu_4_wtd %>% format(digits = 5)`)

College graduate mean (SD): `r mean_edu_5_wtd %>% format(digits = 5)` (`r sd_edu_5_wtd %>% format(digits = 4)`)

### Povery ratio
```{r poverty_reg, include=FALSE}
```

```{r poverty_output, echo=FALSE}
```

Correlation: `r c_pov_wtd`

## Questionnaire

### Doctor Opinion
```{r doctor_tt, include=FALSE}
```

```{r doctor_output, echo=FALSE}
```

ANOVA: 

`r anova_doc_wtd %>% tidy() %>% kable()`

(p value = 3.25e-34)

Pairwise:

`r pw_doc_wtd %>% kable()`

(1st p value = 2.41e-40)

Yes mean (SD): `r mean_doc_yes_wtd %>% format(digits = 5)` (`r sd_doc_yes_wtd %>% format(digits = 5)`)

No mean (SD): `r mean_doc_no_wtd %>% format(digits = 6)` (`r sd_doc_no_wtd %>% format(digits = 5)`)

Don't know mean (SD): `r mean_doc_dont_wtd %>% format(digits = 4)` (`r sd_doc_dont_wtd %>% format(digits = 5)`)

### Sitting minutes
```{r sitting_reg, include=FALSE}
```

```{r sitting_output, echo=FALSE}
```

Correlation: `r c_sit_wtd`

### Vigorous work activity
```{r phys_work_ttest, include=FALSE}
```

```{r phys_work_output, echo=FALSE}
```
T test:

`r ttest_vig_w_wtd %>% tidy() %>% kable()`

Yes mean (SD): `r mean_vig_w_yes_wtd %>% format(digits = 5)` (`r sd_vig_w_yes_wtd %>% format(digits = 4)`)

No mean (SD): `r mean_vig_w_no_wtd %>% format(digits = 5)` (`r sd_vig_w_no_wtd %>% format(digits = 4)`)

### Vigorous recreational activity
```{r phys_rec_tt, include=FALSE}
```

```{r phys_rec_output, echo=FALSE}
```

T test:

`r ttest_vig_r_wtd %>% tidy() %>% kable()`

Yes mean (SD): `r mean_vig_r_yes_wtd %>% format(digits = 5)` (`r sd_vig_r_yes_wtd %>% format(digits = 4)`)

No mean (SD): `r mean_vig_r_no_wtd %>% format(digits = 5)` (`r sd_vig_r_no_wtd %>% format(digits = 4)`)