---
title: "Exploratory Statistics (weighted)"
author: "Christian Hicks"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
pacman::p_load('knitr', 'broom', 'Hmisc', 'survey', 'tidyverse')
knitr::opts_chunk$set(echo = TRUE)
df_combined <- readRDS('./data/combined.Rds')
df_male <- readRDS('./data/male.Rds')
df_female <- readRDS('./data/female.Rds')
svy1 <- svydesign(ids = df_combined$SEQN,
                  weights = df_combined$weight_mec,
                  data = df_combined)
```

## Main study
### Blood Cholesterol
```{r chol, echo=FALSE}
# Histogram
ggplot(df_combined,
       aes(x = bld_tc, weight = weight_mec)
) +
    geom_histogram(
        aes(y = ..density..),
        color = 'black',
        binwidth = 7.5,
        fill = 'grey') +
    stat_density(geom = 'line',
                 aes(color = 'kernal')
    ) +
    stat_function(
        fun = dnorm,
        args = list(
            mean = wtd.mean(df_combined$bld_tc, df_combined$weight_mec),
            sd = wtd.var(df_combined$bld_tc, df_combined$weight_mec) %>% 
              sqrt()),
        aes(color = 'normal')
    ) +
    geom_vline(
      aes(xintercept = svymean(~bld_tc, svy1)[1],
          color = 'mean'),
      size = 1,
      linetype = 'dashed') +
    geom_vline(
      aes(xintercept = as.numeric(svyquantile(~bld_tc,
                                              svy1, 0.5,
                                              ci = F)[1]),
        color = 'median'),
    size = 1,
    linetype = 'dashed'
    ) +
    scale_color_manual(
        name = '',
        values = c(kernal = 'purple',
                   normal = 'black',
                   mean = 'red',
                   median = 'blue'),
    ) +
    ggtitle('Blood Cholesterol distribution') +
    theme(legend.position = 'bottom', legend.direction = 'horizontal') +
    scale_y_continuous(
        sec.axis = sec_axis(trans = ~.*106745272)) +
    xlab('total cholesterol (mg/dL)')
```

### Working hours
```{r work, echo=FALSE}
# Histogram
ggplot(df_combined,
       aes(x = wrk_hrs, weight = weight_mec)
       ) +
  geom_histogram(
    color = 'black',
    binwidth = 5,
    fill = 'grey') +
  ggtitle('Working Hours distribution, weighted study population') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
    geom_vline(
    aes(xintercept = svymean(~wrk_hrs, svy1), color = 'mean'),
    size = 1,
    linetype = 'dashed'
    ) +
  geom_vline(aes(xintercept = as.numeric(svyquantile(
    ~wrk_hrs, svy1, 0.5, ci = F)),
    color = 'median'),
    size = 1,
    linetype = 'dashed'
    ) +
  scale_color_manual(name = 'statistics',
                     values = c(median = 'blue', mean = 'red')) +
  xlab('prior week working hours')

```

## Demographics
### Age
```{r age, echo=FALSE}
# Histogram
ggplot(df_combined,
       aes(x = age, weight = weight_mec)
       ) +
  geom_histogram(
    aes(y = ..density..),
    color = 'black',
    binwidth = 2,
    fill = 'grey') +
  stat_density(geom = 'line',
               aes(color = 'kernal')
               ) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = wtd.mean(df_combined$age, df_combined$weight_mec),
      sd = wtd.var(df_combined$age, df_combined$weight_mec) %>% sqrt()),
    aes(color = 'normal')
    ) +
  geom_vline(
      aes(xintercept = svymean(~age, svy1)[1],
          color = 'mean'),
      size = 1,
      linetype = 'dashed') +
    geom_vline(
      aes(xintercept = as.numeric(svyquantile(~age,
                                              svy1, 0.5,
                                              ci = F)[1]),
        color = 'median'),
    size = 1,
    linetype = 'dashed'
    ) +
  scale_color_manual(
    name = '',
    values = c(kernal = 'purple',
                   normal = 'black',
                   mean = 'red',
                   median = 'blue'),
    ) +
  ggtitle('Age distribution, weighted study population') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
  scale_y_continuous(
    sec.axis = sec_axis(trans = ~.*106745272,
                        name = 'count')
  )

```

### BMI
```{r bmi, echo=FALSE}
# Histogram
ggplot(df_combined,
       aes(x = bmi, weight = weight_mec)
       ) +
  geom_histogram(
    aes(y = ..density..),
    color = 'black',
    binwidth = 2,
    fill = 'grey') +
  stat_density(geom = 'line',
               aes(color = 'kernal')
               ) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = wtd.mean(df_combined$bmi, df_combined$weight_mec),
      sd = wtd.var(df_combined$bmi, df_combined$weight_mec) %>% sqrt()),
    aes(color = 'normal')
    ) +
  geom_vline(
      aes(xintercept = svymean(~bmi, svy1)[1],
          color = 'mean'),
      size = 1,
      linetype = 'dashed') +
    geom_vline(
      aes(xintercept = as.numeric(svyquantile(~bmi,
                                              svy1, 0.5,
                                              ci = F)[1]),
        color = 'median'),
    size = 1,
    linetype = 'dashed'
    ) +
  scale_color_manual(
    name = '',
    values = c(kernal = 'purple',
                   normal = 'black',
                   mean = 'red',
                   median = 'blue'),
    ) +
  ggtitle('BMI distribution, weighted study population') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
  scale_y_continuous(
    sec.axis = sec_axis(trans = ~.*106745272,
                        name = 'count')
  )

```

### Gender
```{r gender, echo=FALSE}
# Bar graph
ggplot(df_combined,
       aes(x = as.factor(gender), weight =weight_mec)) +
  geom_bar(color = 'black',
           fill = 'grey') +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..))),
            stat = 'count',
            color = 'black',
            vjust = -0.5) +
  scale_x_discrete(labels = c('female', 'male')) +
  theme(axis.title.x = element_blank()) +
  labs(title = 'Gender')
```

### Race/Ethnicity
```{r race, echo=FALSE}
# Bar graph
ggplot(df_combined,
       aes(x = as.factor(race_eth), weight =weight_mec)) +
  geom_bar(color = 'black',
           fill = 'grey') +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..))),
            stat = 'count',
            color = 'black',
            vjust = -0.5) +
  scale_x_discrete(labels = c(
    'Mexican American',
    'Other Hispanic',
    'White',
    'Black',
    'Asian',
    'Other'
  )) +
  theme(axis.title.x = element_blank()) +
  labs(title = 'Race/Ethnicity')
```

### Education
```{r education, echo=FALSE}
# Bar graph
ggplot(df_combined,
       aes(x = as.factor(education), weight =weight_mec)) +
  geom_bar(color = 'black',
           fill = 'grey') +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..))),
            stat = 'count',
            color = 'black',
            vjust = -0.5) +
  scale_x_discrete(labels = c('No H.S.',
                              'Some H.S.',
                              'H.S./GED',
                              'Some college',
                              'College',
                              'Refused',
                              'Does not know')) +
  theme(axis.title.x = element_blank()) +
  labs(title = 'Education')
```

### Poverty
```{r poverty, echo=FALSE}
# Histogram
ggplot(df_combined,
       aes(x = income_pov_ratio, weight = weight_mec)
       ) +
  geom_histogram(binwidth = 0.5,
                 na.rm = T,
                 fill = 'grey',
                 color = 'black') +
  labs(x = 'ratio',
       title = 'Income to Poverty Ratio, weighted study population') +
  geom_vline(
    aes(xintercept = svymean(~income_pov_ratio, svy1, na.rm = T), color = 'mean'),
    size = 1,
    linetype = 'dashed') +
  geom_vline(
    aes(xintercept = as.numeric(svyquantile(~income_pov_ratio,
                                            svy1, 0.5,
                                            ci = F,
                                            na.rm = T)[1]),
        color = 'median'),
    size = 1,
    linetype = 'dashed') +
  scale_color_manual(name = 'statistics',
                     values = c(median = 'blue', mean = 'red'))
```

Poverty is based on family size, income, and location. A value of `1` represents the poverty threshold. Ratios over `5` are categorized as `5` to preserve anonymity.

## Questionnaire
### Doctor opinion
```{r doctor_hi, echo=FALSE}
# Bar graph
ggplot(df_combined,
       aes(x = as.factor(chol_doctor_hi), weight =weight_mec)) +
  geom_bar(color = 'black',
           fill = 'grey') +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..))),
            stat = 'count',
            color = 'black',
            vjust = -0.5) +
  scale_x_discrete(labels = c('yes', 'no', 'does not know')) +
  theme(axis.title.x = element_blank()) +
  labs(title = 'Doctor says cholesterol is high, weighted')

```

### Sitting minutes
```{r sit, echo=FALSE}
# Histogram
ggplot(df_combined,
       aes(x = sitting_min_daily, weight = weight_mec)) +
  geom_histogram(binwidth = 65,
                 na.rm = T,
                 color = 'black',
                 fill = 'grey') +
  labs(title = 'Daily sitting minutes, weighted population',
       x = 'minutes',
       y = 'count') +
  geom_vline(
    aes(xintercept = svymean(~sitting_min_daily, svy1, na.rm = T),
        color = 'mean'),
    size = 1,
    linetype = 'dashed') +
  geom_vline(
    aes(xintercept = as.numeric(svyquantile(~sitting_min_daily,
                                            svy1, 0.5,
                                            ci = F,
                                            na.rm = T)[1]),
        color = 'median'),
    size = 1,
    linetype = 'dashed') +
  scale_color_manual(name = 'statistics',
                     values = c(median = 'blue', mean = 'red'))

```

### Vigorous activity at work
```{r phys_work, echo=FALSE}
# Bar graph
ggplot(df_combined,
       aes(x = as.factor(phys_work_vig), weight =weight_mec)) +
  geom_bar(color = 'black',
           fill = 'grey') +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..))),
            stat = 'count',
            color = 'black',
            vjust = -0.5) +
  scale_x_discrete(labels = c('yes', 'no', 'does not know')) +
  theme(axis.title.x = element_blank()) +
  labs(title = 'Vigorous work activity')
```

### Vigorous recreational activity
```{r phys_rec, echo=FALSE}
# Bar graph
ggplot(df_combined,
       aes(x = as.factor(phys_rec_vig), weight =weight_mec)) +
  geom_bar(color = 'black',
           fill = 'grey') +
  geom_text(aes(label = scales::percent((..count..)/sum(..count..))),
            stat = 'count',
            color = 'black',
            vjust = -0.5) +
  scale_x_discrete(labels = c('yes', 'no')) +
  theme(axis.title.x = element_blank()) +
  labs(title = 'Vigorous recreational activity')
```