---
title: "Exploratory Statistics"
author: "Christian Hicks"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
pacman::p_load('knitr', 'broom', 'Hmisc', 'survey', 'tidyverse')
knitr::opts_chunk$set(echo = TRUE)
df_combined <- readRDS('./data/combined.Rds')
df_male <- readRDS('./data/male.Rds')
df_female <- readRDS('./data/female.Rds')
svy1 <- svydesign(ids = df_combined$SEQN,
                  weights = df_combined$weight_mec,
                  data = df_combined)
```

## Main study
### Blood Cholesterol
```{r chol, echo=FALSE}
# Unweighted
ggplot(df_combined,
       aes(x = bld_tc)
       ) +
  geom_histogram(
    aes(y = ..density..),
    color = 'black',
    binwidth = 7.5,
    fill = 'grey') +
  stat_density(geom = 'line',
               aes(color = 'x')
               ) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = mean(df_combined$bld_tc),
      sd = sd(df_combined$bld_tc)),
    aes(color = 'xx')
    ) +
  scale_color_manual(
    name = '',
    values = c('red', 'blue'),
    breaks = c('x', 'xx'),
    labels = c('kernal', 'normal')
    ) +
  ggtitle('Blood Cholesterol distribution, unweighted study population') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
  scale_y_continuous(
    sec.axis = sec_axis(trans = ~.*length(na.omit(df_combined$bld_tc)),
                        name = 'count')
  ) +
  xlab('total cholesterol (mg/dL)')

# Unweighted normal Q-Q plot
qqnorm(df_combined$bld_tc);qqline(df_combined$bld_tc, col = 2)

# Weighted
ggplot(df_combined,
       aes(x = bld_tc, weight = weight_mec)
) +
    geom_histogram(
        aes(y = ..density..),
        color = 'black',
        binwidth = 7.5,
        fill = 'grey') +
    stat_density(geom = 'line',
                 aes(color = 'x')
    ) +
    stat_function(
        fun = dnorm,
        args = list(
            mean = wtd.mean(df_combined$bld_tc, df_combined$weight_mec),
            sd = wtd.var(df_combined$bld_tc, df_combined$weight_mec) %>% 
              sqrt()),
        aes(color = 'xx')
    ) +
    scale_color_manual(
        name = '',
        values = c('red', 'blue'),
        breaks = c('x', 'xx'),
        labels = c('kernal', 'normal')
    ) +
    ggtitle('Blood Cholesterol distribution, weighted study population') +
    theme(legend.position = 'bottom', legend.direction = 'horizontal') +
    scale_y_continuous(
        sec.axis = sec_axis(trans = ~.*106745272)) +
    xlab('total cholesterol (mg/dL)')
```

Shapiro-Wilk normality test for unweighted histogram: p = `r (shapiro.test(df_combined$bld_tc) %>% tidy())[2]`

```{r chol_gender, echo=FALSE}
# Gender split histogram
ggplot(df_combined,
       aes(x = bld_tc,
           color = as.factor(gender),
           fill = as.factor(gender))
       ) +
  geom_histogram(alpha = 1, position = 'dodge', binwidth = 10) +
  scale_color_manual(name = 'Gender',
                     labels = c('Female', 'Male'),
                     values = c('2', 'darkblue'),
                     ) +
    scale_fill_manual(name = 'Gender',
                     labels = c('Female', 'Male'),
                     values = c('lightpink', 'lightblue'),
                     ) +
  ggtitle('Blood TC distribution by gender, unweighted') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
  xlab('total cholesterol (mg/dL)')
```

Male proportion of unweighted study population: `r round(((prop.table(table(df_combined$gender))[2])*100), 1) %>% format(nsmall = 1)`%

```{r chol_table, echo=FALSE}
# Table
tc_tot <- summary(df_combined$bld_tc)[c(1, 3, 4, 6)] %>% round(2)
tc_male <- summary(df_male$bld_tc)[c(1, 3, 4, 6)] %>% round(2)
tc_female <- summary(df_female$bld_tc)[c(1, 3, 4, 6)] %>% round(2)
tc_cats <- c('Min', 'Median', 'Mean', 'Max')
tc_tbl <- tibble(Statistic = tc_cats, 
                   Total = tc_tot, 
                   Male = tc_male, 
                   Female = tc_female)
tc_tbl %>% kable(caption = 'Cholesterol (mg/dL) breakdown, unweighted')
```

Total n = `r length(na.omit(df_combined$bld_tc))`

Male n = `r length(na.omit(df_male$bld_tc))`

Female n = `r length(na.omit(df_female$bld_tc))`

### Working hours
```{r work, echo=FALSE}
# Unweighted
ggplot(df_combined,
       aes(x = wrk_hrs)
       ) +
  geom_histogram(
    color = 'black',
    binwidth = 5,
    fill = 'grey') +
  ggtitle('Working Hours distribution, unweighted study population') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
    geom_vline(
    aes(xintercept = mean(wrk_hrs, na.rm = T), color = 'mean'),
    size = 1,
    linetype = 'dashed'
  ) +
  geom_vline(
    aes(xintercept = median(wrk_hrs, na.rm = T), color = 'median'),
    size = 1,
    linetype = 'dashed'
  ) +
  scale_color_manual(name = 'statistics',
                     values = c(median = 'blue', mean = 'red')) +
  xlab('prior week working hours')

# Weighted
ggplot(df_combined,
       aes(x = wrk_hrs, weight = weight_mec)
       ) +
  geom_histogram(
    color = 'black',
    binwidth = 5,
    fill = 'grey') +
  ggtitle('Working Hours distribution, weighted study population') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
    geom_vline(
    aes(xintercept = svymean(~wrk_hrs, svy1), color = 'mean'),
    size = 1,
    linetype = 'dashed'
    ) +
  geom_vline(aes(xintercept = as.numeric(svyquantile(
    ~wrk_hrs, svy1, 0.5, ci = F)),
    color = 'median'),
    size = 1,
    linetype = 'dashed'
    ) +
  scale_color_manual(name = 'statistics',
                     values = c(median = 'blue', mean = 'red')) +
  xlab('prior week working hours')

# Unweighted gender split histogram
ggplot(df_combined,
       aes(x = wrk_hrs,
           color = as.factor(gender),
           fill = as.factor(gender))
       ) +
  geom_histogram(alpha = 1, position = 'dodge', binwidth = 5) +
  scale_color_manual(name = 'Gender',
                     labels = c('Female', 'Male'),
                     values = c('2', 'darkblue'),
                     ) +
    scale_fill_manual(name = 'Gender',
                     labels = c('Female', 'Male'),
                     values = c('lightpink', 'lightblue'),
                     ) +
  ggtitle('Working Hours distribution by gender, unweighted') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
  xlab('prior week working hours')

# Table
wrk_tot <- summary(df_combined$wrk_hrs)[c(1, 3, 4, 6)] %>% round(2)
wrk_male <- summary(df_male$wrk_hrs)[c(1, 3, 4, 6)] %>% round(2)
wrk_female <- summary(df_female$wrk_hrs)[c(1, 3, 4, 6)] %>% round(2)
wrk_cats <- c('Min', 'Median', 'Mean', 'Max')
wrk_tbl <- tibble(Statistic = wrk_cats, 
                   Total = wrk_tot, 
                   Male = wrk_male, 
                   Female = wrk_female)
wrk_tbl %>% kable(caption = 'Working Hours breakdown, unweighted')

```

Total n = `r length(na.omit(df_combined$wrk_hrs))`

Male n = `r length(na.omit(df_male$wrk_hrs))`

Female n = `r length(na.omit(df_female$wrk_hrs))`

## Demographics
### Age
```{r age, echo=FALSE}
# Unweighted histogram
ggplot(df_combined,
       aes(x = age)
       ) +
  geom_histogram(
    aes(y = ..density..),
    color = 'black',
    binwidth = 2,
    fill = 'grey') +
  stat_density(geom = 'line',
               aes(color = 'x')
               ) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = mean(df_combined$age),
      sd = sd(df_combined$age)),
    aes(color = 'xx')
    ) +
  scale_color_manual(
    name = '',
    values = c('red', 'blue'),
    breaks = c('x', 'xx'),
    labels = c('kernal', 'normal')
    ) +
  ggtitle('Age distribution, unweighted study population') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
  scale_y_continuous(
    sec.axis = sec_axis(trans = ~.*length(na.omit(df_combined$age)),
                        name = 'count')
  )

# Weighted histogram
ggplot(df_combined,
       aes(x = age, weight = weight_mec)
       ) +
  geom_histogram(
    aes(y = ..density..),
    color = 'black',
    binwidth = 2,
    fill = 'grey') +
  stat_density(geom = 'line',
               aes(color = 'x')
               ) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = wtd.mean(df_combined$age, df_combined$weight_mec),
      sd = wtd.var(df_combined$age, df_combined$weight_mec) %>% sqrt()),
    aes(color = 'xx')
    ) +
  scale_color_manual(
    name = '',
    values = c('red', 'blue'),
    breaks = c('x', 'xx'),
    labels = c('kernal', 'normal')
    ) +
  ggtitle('Age distribution, weighted study population') +
  theme(legend.position = 'bottom', legend.direction = 'horizontal') +
  scale_y_continuous(
    sec.axis = sec_axis(trans = ~.*106745272,
                        name = 'count')
  )

# Table
age_tot <- summary(df_combined$age)[c(1, 3, 4, 6)] %>% round(2)
age_male <- summary(df_male$age)[c(1, 3, 4, 6)] %>% round(2)
age_female <- summary(df_female$age)[c(1, 3, 4, 6)] %>% round(2)
age_cats <- c('Min', 'Median', 'Mean', 'Max')
age_tbl <- tibble(Statistic = age_cats, 
                   Total = age_tot, 
                   Male = age_male, 
                   Female = age_female)
age_tbl %>% kable(caption = 'Age breakdown, unweighted')
```

Total n = `r length(na.omit(df_combined$age))`

Male n = `r length(na.omit(df_male$age))`

Female n = `r length(na.omit(df_female$age))`

### Race/Ethnicity
```{r race, echo=FALSE}
race_tot <- round(
  prop.table(table(df_combined$race_eth))
  *100, 2
)
race_male <- round(
  prop.table(table(df_male$race_eth))
  *100, 2
)
race_female <- round(
  prop.table(table(df_female$race_eth))
  *100, 2
)
race_cats <- c('Mexican American',
               'Other Hispanic',
               'Non-Hispanic White',
               'Non-Hispanic Black',
               'Non-Hispanic Asian',
               'Other/Multi-Racial')
race_tbl <- tibble(Category = race_cats, 
                   Total = race_tot, 
                   Male = race_male, 
                   Female = race_female)
race_tbl %>% kable(caption = 'Values in %')
```

Total n = `r length(na.omit(df_combined$race_eth))`

Male n = `r length(na.omit(df_male$race_eth))`

Female n = `r length(na.omit(df_female$race_eth))`

### Education
```{r education, echo=FALSE}
edu_tot <- round(
  prop.table(table(df_combined$education))
  *100, 2
)
edu_male <- round(
  prop.table(table(df_male$education))
  *100, 2
)
# Add NA for the 'Refused' response
edu_male <- c(edu_male[1:5], NA, edu_male[6])

edu_female <- round(
  prop.table(table(df_female$education))
  *100, 2
)
# Add NA for the 'Does not know' response
edu_female <- c(edu_female[1:6], NA)

edu_cats <- c('Less than high school',
              'Incomplete high school',
              'High school or GED',
              'Some college or AA degree',
              'College graduate or above',
              'Refused',
              'Does not know')
edu_tbl <- tibble(Category = edu_cats,
                  Total = edu_tot,
                  Male = edu_male,
                  Female = edu_female)
edu_tbl %>% kable(caption = 'Values in %, unweighted')
```

Total n = `r length(na.omit(df_combined$education))`

Male n = `r length(na.omit(df_male$education))`

Female n = `r length(na.omit(df_female$education))`

### Poverty
```{r poverty, echo=FALSE}
# Unweighted
ggplot(df_combined,
       aes(x = income_pov_ratio)
       ) +
  geom_histogram(binwidth = 0.5,
                 na.rm = T,
                 fill = 'grey',
                 color = 'black') +
  labs(x = 'ratio',
       title = 'Income to Poverty Ratio, unweighted study population') +
  geom_vline(
    aes(xintercept = mean(income_pov_ratio, na.rm = T), color = 'mean'),
    size = 1,
    linetype = 'dashed'
  ) +
  geom_vline(
    aes(xintercept = median(income_pov_ratio, na.rm = T), color = 'median'),
    size = 1,
    linetype = 'dashed'
  ) +
  scale_color_manual(name = 'statistics',
                     values = c(median = 'blue', mean = 'red'))

# Weighted
ggplot(df_combined,
       aes(x = income_pov_ratio, weight = weight_mec)
       ) +
  geom_histogram(binwidth = 0.5,
                 na.rm = T,
                 fill = 'grey',
                 color = 'black') +
  labs(x = 'ratio',
       title = 'Income to Poverty Ratio, weighted study population') +
  geom_vline(
    aes(xintercept = svymean(~income_pov_ratio, svy1, na.rm = T), color = 'mean'),
    size = 1,
    linetype = 'dashed') +
  geom_vline(
    aes(xintercept = as.numeric(svyquantile(~income_pov_ratio,
                                            svy1, 0.5,
                                            ci = F,
                                            na.rm = T)[1]),
        color = 'median'),
    size = 1,
    linetype = 'dashed') +
  scale_color_manual(name = 'statistics',
                     values = c(median = 'blue', mean = 'red'))
```

Poverty is based on family size, income, and location. A value of `1` represents the poverty threshold. Ratios over `5` are categorized as `5` to preserve anonymity.

```{r poverty_gender, echo=FALSE}
# Organized as: total, male, female
pov_tot <- summary(df_combined$income_pov_ratio)[c(1, 3, 4, 6)] %>% 
  round(2)
pov_male <- summary(df_male$income_pov_ratio)[c(1, 3, 4, 6)] %>% 
  round(2)
pov_female <- summary(df_female$income_pov_ratio)[c(1, 3, 4, 6)] %>% 
  round(2)
pov_cats <- c('Min', 'Median', 'Mean', 'Max')
pov_tbl <- tibble(Statistic = pov_cats, 
                   Total = pov_tot, 
                   Male = pov_male, 
                   Female = pov_female)
pov_tbl %>% kable(caption = 'Poverty Ratios, unweighted')
```

Total n = `r length(na.omit(df_combined$income_pov_ratio))`

Male n = `r length(na.omit(df_male$income_pov_ratio))`

Female n = `r length(na.omit(df_female$income_pov_ratio))`

## Questionnaire
### Doctor opinion
```{r doctor_hi, echo=FALSE}
# Unweighted
ggplot(df_combined,
       aes(x = as.factor(chol_doctor_hi))) +
  geom_bar(color = 'black',
           fill = 'grey') +
  geom_text(aes(label = ..count..),
            stat = 'count',
            color = 'black',
            vjust = -0.5) +
  scale_x_discrete(labels = c('yes', 'no', 'does not know')) +
  theme(axis.title.x = element_blank()) +
  labs(title = 'Doctor says cholesterol is high, unweighted')

# Weighted
ggplot(df_combined,
       aes(x = as.factor(chol_doctor_hi), weight =weight_mec)) +
  geom_bar(color = 'black',
           fill = 'grey') +
  geom_text(aes(label = format(..count..), digits = 1),
            stat = 'count',
            color = 'black',
            vjust = -0.5) +
  scale_x_discrete(labels = c('yes', 'no', 'does not know')) +
  theme(axis.title.x = element_blank()) +
  labs(title = 'Doctor says cholesterol is high, weighted')

doc_tot <- round(
  prop.table(table(df_combined$chol_doctor_hi))
  *100, 2
)
doc_male <- round(
  prop.table(table(df_male$chol_doctor_hi))
  *100, 2
)
doc_female <- round(
  prop.table(table(df_female$chol_doctor_hi))
  *100, 2
)
doc_cats <- c('Yes', 'No', 'Does not know')

doc_tbl <- tibble(Category = doc_cats,
                  Total = doc_tot,
                  Male = doc_male,
                  Female = doc_female)

doc_tbl %>% kable(caption = 'Values in %, unweighted')
```

Total n = `r length(na.omit(df_combined$chol_doctor_hi))`

Male n = `r length(na.omit(df_male$chol_doctor_hi))`

Female n = `r length(na.omit(df_female$chol_doctor_hi))`

### Sitting minutes
```{r sit, echo=FALSE}
# Unweighted
qplot(df_combined$sitting_min_daily,
      binwidth = 65,
      na.rm = T,
      color = I('black'),
      fill = I('grey')) +
    labs(title = 'Daily sitting minutes, unweighted population',
       x = 'minutes',
       y = 'count')

# Weighted
ggplot(df_combined,
       aes(x = sitting_min_daily, weight = weight_mec)) +
  geom_histogram(binwidth = 65,
                 na.rm = T,
                 color = 'black',
                 fill = 'grey') +
  labs(title = 'Daily sitting minutes, weighted population',
       x = 'minutes',
       y = 'count')

# Table
sit_tot <- summary(df_combined$sitting_min_daily)[c(1, 3, 4, 6)] %>% 
  round(2)
sit_male <- summary(df_male$sitting_min_daily)[c(1, 3, 4, 6)] %>% 
  round(2)
sit_female <- summary(df_female$sitting_min_daily)[c(1, 3, 4, 6)] %>% 
  round(2)
sit_tot <- sit_tot %>% 
  round(2)
sit_male <- sit_male %>% 
  round(2)
sit_female <- sit_female %>% 
  round(2)
sit_cats <- c('Min', 'Median', 'Mean', 'Max')
sit_tbl <- tibble(Statistic = sit_cats, 
                   Total = sit_tot, 
                   Male = sit_male, 
                   Female = sit_female)
sit_tbl %>% kable(caption = 'Gender breakdown, unweighted')
```

Total n = `r length(na.omit(df_combined$sitting_min_daily))`

Male n = `r length(na.omit(df_male$sitting_min_daily))`

Female n = `r length(na.omit(df_female$sitting_min_daily))`

### Vigorous activity at work
```{r phys_work, echo=FALSE}
phys_w_tot <- round(
  prop.table(table(df_combined$phys_work_vig))
  *100, 2
)
phys_w_male <- round(
  prop.table(table(df_male$phys_work_vig))
  *100, 2
)
# Add NA for the 'Does not know' column
phys_w_male <- c(phys_w_male, NA)
phys_w_female <- round(
  prop.table(table(df_female$phys_work_vig))
  *100, 2
)
phys_w_cats <- c('Yes', 'No', 'Does not know')

phys_w_tbl <- tibble(Category = phys_w_cats,
                  Total = phys_w_tot,
                  Male = phys_w_male,
                  Female = phys_w_female)

phys_w_tbl %>% kable(caption = 'Values in %, unweighted')

```

Total n = `r length(na.omit(df_combined$phys_work_vig))`

Male n = `r length(na.omit(df_male$phys_work_vig))`

Female n = `r length(na.omit(df_female$phys_work_vig))`

### Vigorous recreational activity
```{r phys_rec, echo=FALSE}
phys_r_tot <- round(
  prop.table(table(df_combined$phys_rec_vig))
  *100, 2
)
phys_r_male <- round(
  prop.table(table(df_male$phys_rec_vig))
  *100, 2
)
phys_r_female <- round(
  prop.table(table(df_female$phys_rec_vig))
  *100, 2
)
phys_r_cats <- c('Yes', 'No')

phys_r_tbl <- tibble(Category = phys_r_cats,
                  Total = phys_r_tot,
                  Male = phys_r_male,
                  Female = phys_r_female)

phys_r_tbl %>% kable(caption = 'Values in %, unweighted')

```

Total n = `r length(na.omit(df_combined$phys_rec_vig))`

Male n = `r length(na.omit(df_male$phys_rec_vig))`

Female n = `r length(na.omit(df_female$phys_rec_vig))`