---
title: "Bivariate Analysis"
author: "Christian Hicks"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load('knitr', 'broom', 'survey', 'tidyverse')
df_combined <- readRDS('./data/combined.Rds')
attach(df_combined)

# Factorizing variables
gender <- as.factor(gender)
chol_doctor_hi <- as.factor(chol_doctor_hi)
phys_work_vig <- as.factor(phys_work_vig)
phys_rec_vig <- as.factor(phys_rec_vig)
race_eth <- as.factor(race_eth)
education <- as.factor(education)
chol_label <- 'total cholesterol (mg/dL)'
quant <- c(0.25, 0.5, 0.75)

# Weighted data
svy1 <- svydesign(ids = df_combined$SEQN,
                  weights = df_combined$weight_mec,
                  data = df_combined)
```

## Working Hours

```{r wrk_hrs, include=FALSE}
# Unweighted
plot_wrk <- qplot(wrk_hrs, bld_tc) +
  geom_smooth(formula = y ~ x, method = 'lm') +
  labs(x = 'working hours', y = chol_label, title = 'Cholesterol by working hours, unweighted')
model_wrk <- glm(bld_tc ~ wrk_hrs)
model_wrk_tbl <- model_wrk %>% tidy(conf.int = T)
model_wrk_tbl[2, 1] <- 'Working hours'
model_wrk_tbl <- model_wrk_tbl %>% kable(format = 'markdown', digits = 3)
# Correlation
c_wrk <- cor(bld_tc, wrk_hrs) %>% format(digits = 3)

# Weighted
plot_wrk_wtd <- qplot(wrk_hrs, bld_tc, weight = weight_mec) +
  geom_smooth(formula = y ~ x, method = 'lm') +
  labs(x = 'working hours', y = chol_label, title = 'Cholesterol by working hours, weighted')
model_wrk_wtd <- svyglm(bld_tc ~ wrk_hrs, svy1)
model_wrk_tbl_wtd <- model_wrk_wtd %>% tidy(conf.int = T)
model_wrk_tbl_wtd[2, 1] <- 'Working hours'
model_wrk_tbl_wtd <- model_wrk_tbl_wtd %>% kable(format = 'markdown', digits = 3)
# Correlation
v_wrk_wtd <- svyvar(~bld_tc + wrk_hrs, svy1)
c_wrk_wtd <- cov2cor(as.matrix(v_wrk_wtd))[1, 2] %>% format(digits = 3)
```

### Unweighted
```{r wrk_hrs2, echo=FALSE}
plot_wrk
model_wrk_tbl
```

Correlation: `r c_wrk`

### Weighted
```{r wrk_hrs3, echo=FALSE}
plot_wrk_wtd
model_wrk_tbl_wtd
```

Correlation: `r c_wrk_wtd`

## Age

```{r age, include=FALSE}
# Unweighted
plot_age <- qplot(age, bld_tc) +
  geom_smooth(formula = y ~ x, method = 'lm') +
  labs(x = 'age', y = chol_label, title = 'Cholesterol by age, unweighted')
model_age <- glm(bld_tc ~ age)
model_age_tbl <- model_age %>% tidy(conf.int = T)
model_age_tbl[2, 1] <- 'Age'
model_age_tbl$p.value <- format(model_age_tbl$p.value, digits = 3)
model_age_tbl <- model_age_tbl %>% 
  kable(format = 'markdown', digits = 3)
# Correlation
c_age <- cor(bld_tc, age) %>% format(digits = 3)

# Weighted
plot_age_wtd <- qplot(age, bld_tc, weight = weight_mec) +
  geom_smooth(formula = y ~ x, method = 'lm') +
  labs(x = 'age', y = chol_label, title = 'Cholesterol by age, weighted')
model_age_wtd <- svyglm(bld_tc ~ age, svy1)
model_age_tbl_wtd <- model_age_wtd %>% tidy(conf.int = T)
model_age_tbl_wtd[2, 1] <- 'Age'
model_age_tbl_wtd$p.value <- format(model_age_tbl_wtd$p.value, digits = 3)
model_age_tbl_wtd <- model_age_tbl_wtd %>% 
  kable(format = 'markdown', digits = 3)
# Correlation
v_age_wtd <- svyvar(~bld_tc + age, svy1)
c_age_wtd <- cov2cor(as.matrix(v_age_wtd))[1, 2] %>% format(digits = 3)
```

### Unweighted
```{r age2, echo=FALSE}
plot_age
model_age_tbl
```

Correlation: `r c_age`

### Weighted
```{r age3, echo=FALSE}
plot_age_wtd
model_age_tbl_wtd
```

Correlation: `r c_age_wtd`

## Gender

```{r gender, include=FALSE}
# Unweighted
plot_gender <- qplot(gender, bld_tc,
                     geom = 'violin',
                     draw_quantiles = quant,
                     fill = gender) +
  scale_x_discrete(labels = c('female', 'male')) +
  scale_fill_manual(values = c('lightpink', 'lightblue')) +
  theme(legend.position = 'none') +
  labs(x = 'gender',
       y = chol_label,
       title = 'Cholesterol by gender, unweighted')
# Female is reference; CDC states they have lower LDL and higher HDL
model_gender <- glm(bld_tc ~ gender)
model_gender_tbl <- model_gender %>% tidy(conf.int = T)
model_gender_tbl[2, 1] <- 'Male'
model_gender_tbl <- model_gender_tbl %>% kable(format = 'markdown',
                                               digits = c(3, 3, 3, 3, 4, 3, 3))
# T test
ttest_gen <- t.test(bld_tc ~ gender)
mean_gen_f <- mean(subset(df_combined, gender == 0)$bld_tc)
sd_gen_f <- sd(subset(df_combined, gender == 0)$bld_tc)
mean_gen_m <- mean(subset(df_combined, gender == 1)$bld_tc)
sd_gen_m <- sd(subset(df_combined, gender == 1)$bld_tc)

# Weighted
plot_gender_wtd <- qplot(gender,
                         bld_tc,
                         weight = weight_mec,
                         geom = 'violin',
                         draw_quantiles = quant,
                         fill = gender) +
  scale_x_discrete(labels = c('female', 'male')) +
  scale_fill_manual(values = c('lightpink', 'lightblue')) +
  theme(legend.position = 'none') +
  labs(x = 'gender',
       y = chol_label,
       title = 'Cholesterol by gender, weighted')
# Female is reference; CDC states they have lower LDL and higher HDL
model_gender_wtd <- svyglm(bld_tc ~ gender, svy1)
model_gender_tbl_wtd <- model_gender_wtd %>% tidy(conf.int = T)
model_gender_tbl_wtd[2, 1] <- 'Male'
model_gender_tbl_wtd <- model_gender_tbl_wtd %>% kable(format = 'markdown',
                                                       digits = 3)
# T test
ttest_gen_wtd <- svyttest(bld_tc ~ gender, svy1)
mean_gen_f_wtd <- svymean(~bld_tc, subset(svy1, gender == 0))
sd_gen_f_wtd <- svyvar(~bld_tc, subset(svy1, gender == 0))[1] %>% sqrt()
mean_gen_m_wtd <- svymean(~bld_tc, subset(svy1, gender == 1))
sd_gen_m_wtd <- svyvar(~bld_tc, subset(svy1, gender == 1))[1] %>% sqrt()
```

### Unweighted
```{r gender2, echo=FALSE}
plot_gender
model_gender_tbl
```

T test:

`r ttest_gen %>% tidy() %>% kable()`

Female mean (SD): `r mean_gen_f %>% format(digits = 5)` (`r sd_gen_f %>% format(digits = 4)`)

Male mean (SD): `r mean_gen_m %>% format(digits = 5)` (`r sd_gen_m %>% format(digits = 4)`)

### Weighted
```{r gender3, echo=FALSE}
plot_gender_wtd
model_gender_tbl_wtd
```

T test:

`r ttest_gen_wtd %>% tidy() %>% kable()`

Female mean (SD): `r mean_gen_f_wtd[1] %>% format(digits = 5)` (`r sd_gen_f_wtd %>% format(digits = 4)`)

Male mean (SD): `r mean_gen_m_wtd[1] %>% format(digits = 5)` (`r sd_gen_m_wtd %>% format(digits = 5)`)

## Doctor Opinion

```{r doc, include=FALSE}
# Unweighted
plot_doc <- qplot(reorder(chol_doctor_hi, bld_tc, median), bld_tc,
                  geom = 'violin',
                  draw_quantiles = quant,
                  fill = chol_doctor_hi) +
  scale_x_discrete(labels = c('No (reference)', 'Does not know', 'Yes')) +
  theme(legend.position = 'none') +
  labs(x = 'doctor says cholesterol is high',
       y = chol_label,
       title = 'Cholesterol by response, unweighted')
model_doc <- glm(bld_tc ~ relevel(chol_doctor_hi, ref = '2'))
model_doc_tbl <- model_doc %>% tidy()
model_doc_tbl[2, 1] <- 'Yes'
model_doc_tbl[3, 1] <- 'Does not know'
model_doc_tbl <- model_doc_tbl %>% 
  kable(format = 'markdown', digits = c(3, 3, 3, 3, 4))
# ANOVA
anova_doc <- aov(bld_tc ~ chol_doctor_hi)
pw_doc <- pairwise.t.test(bld_tc,
                          chol_doctor_hi,
                          p.adjust.method = 'bonf') %>% 
  tidy()
pw_doc[1, 1] <- 'No'
pw_doc[1, 2] <- 'Yes'
pw_doc[2, 1] <- 'Does not know'
pw_doc[2, 2] <- 'Yes'
pw_doc[3, 1] <- 'Does not know'
pw_doc[3, 2] <- 'No'
mean_doc_yes <- mean(subset(df_combined, chol_doctor_hi == 1)$bld_tc)
sd_doc_yes <- sd(subset(df_combined, chol_doctor_hi == 1)$bld_tc)
mean_doc_no <- mean(subset(df_combined, chol_doctor_hi == 2)$bld_tc)
sd_doc_no <- sd(subset(df_combined, chol_doctor_hi == 2)$bld_tc)
mean_doc_dont <- mean(subset(df_combined, chol_doctor_hi == 9)$bld_tc)
sd_doc_dont <- sd(subset(df_combined, chol_doctor_hi == 9)$bld_tc)

#Weighted
plot_doc_wtd <- qplot(reorder(chol_doctor_hi, bld_tc, median), bld_tc,
                  weight = weight_mec,
                  geom = 'violin',
                  draw_quantiles = quant,
                  fill = chol_doctor_hi) +
  scale_x_discrete(labels = c('No (reference)', 'Does not know', 'Yes')) +
  theme(legend.position = 'none') +
  labs(x = 'doctor says cholesterol is high',
       y = chol_label,
       title = 'Cholesterol by response, weighted')
model_doc_wtd <- svyglm(bld_tc ~ relevel(as.factor(chol_doctor_hi), ref = '2'), 
                        svy1)
model_doc_tbl_wtd <- model_doc_wtd %>% tidy()
model_doc_tbl_wtd[2, 1] <- 'Yes'
model_doc_tbl_wtd[3, 1] <- 'Does not know'
model_doc_tbl_wtd <- model_doc_tbl_wtd %>% 
  kable(format = 'markdown', digits = c(3, 3, 3, 3, 4))
# ANOVA
anova_doc_wtd <- aov(bld_tc ~ chol_doctor_hi, weights = weight_mec)
pw_doc_wtd <- pairwise.t.test(bld_tc, chol_doctor_hi,
                              weights = weight_mec,
                              p.adjust.method = 'bonf') %>% 
  tidy()
pw_doc_wtd[1, 1] <- 'No'
pw_doc_wtd[1, 2] <- 'Yes'
pw_doc_wtd[2, 1] <- 'Does not know'
pw_doc_wtd[2, 2] <- 'Yes'
pw_doc_wtd[3, 1] <- 'Does not know'
pw_doc_wtd[3, 2] <- 'No'
mean_doc_yes_wtd <- svymean(~bld_tc, subset(svy1, chol_doctor_hi == 1))
sd_doc_yes_wtd <- svyvar(~bld_tc, subset(svy1, chol_doctor_hi == 1))[1] %>% 
  sqrt()
mean_doc_no_wtd <- svymean(~bld_tc, subset(svy1, chol_doctor_hi == 2))
sd_doc_no_wtd <- svyvar(~bld_tc, subset(svy1, chol_doctor_hi == 2))[1] %>% 
  sqrt()
mean_doc_dont_wtd <- svymean(~bld_tc, subset(svy1, chol_doctor_hi == 9))
sd_doc_dont_wtd <- svyvar(~bld_tc, subset(svy1, chol_doctor_hi == 9))[1] %>% 
  sqrt()
```

### Unweighted
```{r doc2, echo=FALSE}
plot_doc
model_doc_tbl
```

ANOVA: 

`r anova_doc %>% tidy() %>% kable()`

Pairwise:

`r pw_doc %>% kable()`

No mean (SD): `r mean_doc_no %>% format(digits = 6)` (`r sd_doc_no %>% format(digits = 5)`)

Don't know mean (SD): `r mean_doc_dont %>% format(digits = 4)` (`r sd_doc_dont %>% format(digits = 5)`)

Yes mean (SD): `r mean_doc_yes %>% format(digits = 5)` (`r sd_doc_yes %>% format(digits = 5)`)

### Weighted
```{r doc3, echo=FALSE}
plot_doc_wtd
model_doc_tbl_wtd
```

ANOVA: 

`r anova_doc_wtd %>% tidy() %>% kable()`

(p value = 3.25e-34)

Pairwise:

`r pw_doc_wtd %>% kable()`

(1st p value = 2.41e-40)

Yes mean (SD): `r mean_doc_yes_wtd %>% format(digits = 5)` (`r sd_doc_yes_wtd %>% format(digits = 5)`)

No mean (SD): `r mean_doc_no_wtd %>% format(digits = 6)` (`r sd_doc_no_wtd %>% format(digits = 5)`)

Don't know mean (SD): `r mean_doc_dont_wtd %>% format(digits = 4)` (`r sd_doc_dont_wtd %>% format(digits = 5)`)

## Sitting minutes
```{r sit, include=FALSE}
# Unweighted
plot_sit <- qplot(sitting_min_daily, bld_tc) +
  geom_smooth(formula = y ~ x, method = 'lm') +
  labs(x = 'daily sitting minutes',
       y = chol_label,
       title = 'Cholesterol by sitting minutes, unweighted')
model_sit <- glm(bld_tc ~ sitting_min_daily)
model_sit_tbl <- model_sit %>% tidy(conf.int = T)
model_sit_tbl[2, 1] <- 'Sitting minutes'
model_sit_tbl$p.value <- format(model_sit_tbl$p.value, digits = 3)
model_sit_tbl <- model_sit_tbl %>% 
  kable(format = 'markdown', digits = 3)
# Correlation
c_sit <- cor(bld_tc,
             sitting_min_daily,
             use = 'complete.obs') %>% 
  format(digits = 3)

# Weighted
plot_sit_wtd <- qplot(sitting_min_daily, bld_tc, weight = weight_mec) +
  geom_smooth(formula = y ~ x, method = 'lm') +
  labs(x = 'daily sitting minutes',
       y = chol_label,
       title = 'Cholesterol by sitting minutes, weighted')
model_sit_wtd <- svyglm(bld_tc ~ sitting_min_daily, svy1)
model_sit_tbl_wtd <- model_sit_wtd %>% tidy(conf.int = T)
model_sit_tbl_wtd[2, 1] <- 'Sitting minutes'
model_sit_tbl_wtd$p.value <- format(model_sit_tbl_wtd$p.value, digits = 3)
model_sit_tbl_wtd <- model_sit_tbl_wtd %>% 
  kable(format = 'markdown', digits = 3)
# Correlation
v_sit_wtd <- svyvar(~bld_tc + sitting_min_daily, 
                    svy1,
                    na.rm = T)
c_sit_wtd <- cov2cor(as.matrix(v_sit_wtd))[1, 2] %>% format(digits = 3)
```

### Unweighted
```{r sit2, echo=FALSE}
plot_sit
model_sit_tbl
```

Correlation: `r c_sit`

### Weighted
```{r sit3, echo=FALSE}
plot_sit_wtd
model_sit_tbl_wtd
```

Correlation: `r c_sit_wtd`

## Vigorous work activity
```{r vig_w, include = FALSE}
# Weighted
plot_vig_w_wtd <- qplot(reorder(phys_work_vig, bld_tc, median),
                        bld_tc,
                        weight = weight_mec,
                        geom = 'violin',
                        draw_quantiles = quant,
                        fill = phys_work_vig) +
  scale_x_discrete(labels = c('Does not know', 'Yes', 'No (reference)')) +
  theme(legend.position = 'none') +
  labs(x = 'vigorous physical activity at work',
       y = chol_label,
       title = 'Cholesterol by response, weighted')
model_vig_w_wtd <- svyglm(bld_tc ~ relevel(as.factor(phys_work_vig), ref = '2'), 
                        svy1)
model_vig_w_tbl_wtd <- model_vig_w_wtd %>% tidy()
model_vig_w_tbl_wtd[2, 1] <- 'Yes'
model_vig_w_tbl_wtd[3, 1] <- 'Does not know'
model_vig_w_tbl_wtd <- model_vig_w_tbl_wtd %>% 
  kable()
# ANOVA
anova_vig_w_wtd <- aov(bld_tc ~ phys_work_vig, weights = weight_mec)
mean_vig_w_yes_wtd <- svymean(~bld_tc, subset(svy1, phys_work_vig == 1))
sd_vig_w_yes_wtd <- svyvar(~bld_tc, subset(svy1, phys_work_vig == 1))[1] %>% 
  sqrt()
mean_vig_w_no_wtd <- svymean(~bld_tc, subset(svy1, phys_work_vig == 2))
sd_vig_w_no_wtd <- svyvar(~bld_tc, subset(svy1, phys_work_vig == 2))[1] %>% 
  sqrt()
mean_vig_w_dont_wtd <- svymean(~bld_tc, subset(svy1, phys_work_vig == 9))
sd_vig_w_dont_wtd <- svyvar(~bld_tc, subset(svy1, phys_work_vig == 9))[1] %>% 
  sqrt()
```

### Weighted
```{r vig_w2, echo=FALSE}
plot_vig_w_wtd
model_vig_w_tbl_wtd
```

ANOVA:

`r anova_vig_w_wtd %>% tidy() %>% kable()`

Yes mean (SD): `r mean_vig_w_yes_wtd %>% format(digits = 5)` (`r sd_vig_w_yes_wtd %>% format(digits = 4)`)

No mean (SD): `r mean_vig_w_no_wtd %>% format(digits = 5)` (`r sd_vig_w_no_wtd %>% format(digits = 4)`)

Don't know mean (SD): `r mean_vig_w_dont_wtd %>% format(digits = 3)` (`r sd_vig_w_dont_wtd %>% format(digits = 4)`) (1 obs)

## Vigorous recreational activity
```{r vig_r, include = FALSE}
# Weighted
plot_vig_r_wtd <- qplot(reorder(phys_rec_vig, bld_tc, median),
                        bld_tc,
                        weight = weight_mec,
                        geom = 'violin',
                        draw_quantiles = quant,
                        fill = phys_rec_vig) +
  scale_x_discrete(labels = c('Yes', 'No (reference)')) +
  theme(legend.position = 'none') +
  labs(x = 'vigorous physical recreational activity',
       y = chol_label,
       title = 'Cholesterol by response, weighted')
model_vig_r_wtd <- svyglm(bld_tc ~ relevel(as.factor(phys_rec_vig), ref = '2'),
                          svy1)
model_vig_r_tbl_wtd <- model_vig_r_wtd %>% tidy()
model_vig_r_tbl_wtd[2, 1] <- 'Yes'
model_vig_r_tbl_wtd <- model_vig_r_tbl_wtd %>% 
  kable()
# T test
ttest_vig_r_wtd <- svyttest(bld_tc ~ phys_rec_vig, svy1)
mean_vig_r_yes_wtd <- svymean(~bld_tc, subset(svy1, phys_rec_vig == 1))
sd_vig_r_yes_wtd <- svyvar(~bld_tc, subset(svy1, phys_rec_vig == 1))[1] %>% 
  sqrt()
mean_vig_r_no_wtd <- svymean(~bld_tc, subset(svy1, phys_rec_vig == 2))
sd_vig_r_no_wtd <- svyvar(~bld_tc, subset(svy1, phys_rec_vig == 2))[1] %>% 
  sqrt()
```

### Weighted
```{r vig_r2, echo=FALSE}
plot_vig_r_wtd
model_vig_r_tbl_wtd
```

T test:

`r ttest_vig_r_wtd %>% tidy() %>% kable()`

Yes mean (SD): `r mean_vig_r_yes_wtd %>% format(digits = 5)` (`r sd_vig_r_yes_wtd %>% format(digits = 4)`)

No mean (SD): `r mean_vig_r_no_wtd %>% format(digits = 5)` (`r sd_vig_r_no_wtd %>% format(digits = 4)`)

## Race/Ethnicity
```{r race, include = FALSE}
# Weighted
plot_race_wtd <- qplot(reorder(race_eth, bld_tc, median), bld_tc,
                  weight = weight_mec,
                  geom = 'violin',
                  draw_quantiles = quant,
                  fill = race_eth) +
  scale_x_discrete(labels = c('Black',
                              'White (reference)',
                              'Other Hispanic',
                              'Mexican American',
                              'Other or Multi',
                              'Asian')) +
  theme(legend.position = 'none') +
  labs(x = 'race/ethnicity',
       y = chol_label,
       title = 'Cholesterol by race/ethnicity, weighted')
model_race_wtd <- svyglm(bld_tc ~ relevel(as.factor(race_eth), ref = '3'), 
                        svy1)
model_race_tbl_wtd <- model_race_wtd %>% tidy()
model_race_tbl_wtd[2, 1] <- 'Mexican American'
model_race_tbl_wtd[3, 1] <- 'Other Hispanic'
model_race_tbl_wtd[4, 1] <- 'Non-Hispanic Black'
model_race_tbl_wtd[5, 1] <- 'Non-Hispanic Asian'
model_race_tbl_wtd[6, 1] <- 'Other race or Multi-Racial'
model_race_tbl_wtd <- model_race_tbl_wtd %>% 
  kable()
# ANOVA
anova_race_wtd <- aov(bld_tc ~ race_eth, weights = weight_mec)
pw_race_wtd <- pairwise.t.test(bld_tc, race_eth,
                               weights = weight_mec,
                               p.adjust.method = 'bonf') %>% 
  tidy()
mean_race_1_wtd <- svymean(~bld_tc, subset(svy1, race_eth == 1))
sd_race_1_wtd <- svyvar(~bld_tc, subset(svy1, race_eth == 1))[1] %>% 
  sqrt()
mean_race_2_wtd <- svymean(~bld_tc, subset(svy1, race_eth == 2))
sd_race_2_wtd <- svyvar(~bld_tc, subset(svy1, race_eth == 2))[1] %>% 
  sqrt()
mean_race_3_wtd <- svymean(~bld_tc, subset(svy1, race_eth == 3))
sd_race_3_wtd <- svyvar(~bld_tc, subset(svy1, race_eth == 3))[1] %>% 
  sqrt()
mean_race_4_wtd <- svymean(~bld_tc, subset(svy1, race_eth == 4))
sd_race_4_wtd <- svyvar(~bld_tc, subset(svy1, race_eth == 4))[1] %>% 
  sqrt()
mean_race_6_wtd <- svymean(~bld_tc, subset(svy1, race_eth == 6))
sd_race_6_wtd <- svyvar(~bld_tc, subset(svy1, race_eth == 6))[1] %>% 
  sqrt()
mean_race_7_wtd <- svymean(~bld_tc, subset(svy1, race_eth == 7))
sd_race_7_wtd <- svyvar(~bld_tc, subset(svy1, race_eth == 7))[1] %>% 
  sqrt()
```

### Weighted
```{r race2, echo=FALSE}
plot_race_wtd
model_race_tbl_wtd
```

ANOVA:

`r anova_race_wtd %>% tidy() %>% kable()`

Pairwise:

`r pw_race_wtd %>% kable()`

Mexican American mean (SD): `r mean_race_1_wtd %>% format(digits = 6)` (`r sd_race_1_wtd %>% format(digits = 4)`)

Other Hispanic mean (SD): `r mean_race_2_wtd %>% format(digits = 5)` (`r sd_race_2_wtd %>% format(digits = 4)`)

Non-Hispanic White mean (SD): `r mean_race_3_wtd %>% format(digits = 5)` (`r sd_race_3_wtd %>% format(digits = 4)`)

Non-Hispanic Black mean (SD): `r mean_race_4_wtd %>% format(digits = 5)` (`r sd_race_4_wtd %>% format(digits = 5)`)

Non-Hispanic Asian mean (SD): `r mean_race_6_wtd %>% format(digits = 5)` (`r sd_race_6_wtd %>% format(digits = 4)`)

Other race or Multi-Racial mean (SD): `r mean_race_7_wtd %>% format(digits = 5)` (`r sd_race_7_wtd %>% format(digits = 4)`)

## Education
```{r edu, include = FALSE}
# Weighted
plot_edu_wtd <- qplot(reorder(education, bld_tc, median),
                       bld_tc,
                       data = subset(df_combined, !is.na(education)),
                       weight = weight_mec,geom = 'violin',
                       draw_quantiles = quant,
                       fill = as.factor(education)) +
  scale_x_discrete(labels = c('H.S. no diploma',
                              'Some college',
                              'H.S./GED (reference)',
                              'College graduate',
                              'No H.S.',
                              'Does not know',
                              'Refused')) +
  theme(legend.position = 'none') +
  labs(x = 'education',
       y = chol_label,
       title = 'Cholesterol by education, weighted')
model_edu_wtd <- svyglm(bld_tc ~ relevel(as.factor(education), ref = '3'), 
                        svy1)
model_edu_tbl_wtd <- model_race_wtd %>% tidy()
model_edu_tbl_wtd[2, 1] <- 'No H.S.'
model_edu_tbl_wtd[3, 1] <- 'H.S. no diploma'
model_edu_tbl_wtd[4, 1] <- 'Some college'
model_edu_tbl_wtd[5, 1] <- 'College graduate'
model_edu_tbl_wtd[6, 1] <- 'Refused'
model_edu_tbl_wtd[7, 1] <- 'Does not know'
model_edu_tbl_wtd <- model_edu_tbl_wtd %>% kable()
# ANOVA
anova_edu_wtd <- aov(bld_tc ~ education, weights = weight_mec)
mean_edu_1_wtd <- svymean(~bld_tc, subset(svy1, education == 1))
sd_edu_1_wtd <- svyvar(~bld_tc, subset(svy1, education == 1))[1] %>% 
  sqrt()
mean_edu_2_wtd <- svymean(~bld_tc, subset(svy1, education == 2))
sd_edu_2_wtd <- svyvar(~bld_tc, subset(svy1, education == 2))[1] %>% 
  sqrt()
mean_edu_3_wtd <- svymean(~bld_tc, subset(svy1, education == 3))
sd_edu_3_wtd <- svyvar(~bld_tc, subset(svy1, education == 3))[1] %>% 
  sqrt()
mean_edu_4_wtd <- svymean(~bld_tc, subset(svy1, education == 4))
sd_edu_4_wtd <- svyvar(~bld_tc, subset(svy1, education == 4))[1] %>% 
  sqrt()
mean_edu_5_wtd <- svymean(~bld_tc, subset(svy1, education == 5))
sd_edu_5_wtd <- svyvar(~bld_tc, subset(svy1, education == 5))[1] %>% 
  sqrt()
mean_edu_7_wtd <- svymean(~bld_tc, subset(svy1, education == 7))
sd_edu_7_wtd <- svyvar(~bld_tc, subset(svy1, education == 7))[1] %>% 
  sqrt()
mean_edu_9_wtd <- svymean(~bld_tc, subset(svy1, education == 9))
sd_edu_9_wtd <- svyvar(~bld_tc, subset(svy1, education == 9))[1] %>% 
  sqrt()
```

### Weighted
```{r edu2, echo=FALSE}
plot_edu_wtd
model_edu_tbl_wtd
```

ANOVA:

`r anova_edu_wtd %>% tidy() %>% kable()`

No H.S. mean (SD): `r mean_edu_1_wtd %>% format(digits = 5)` (`r sd_edu_1_wtd %>% format(digits = 4)`)

H.S. no diploma mean (SD): `r mean_edu_2_wtd %>% format(digits = 5)` (`r sd_edu_2_wtd %>% format(digits = 4)`)

H.S. or GED mean (SD): `r mean_edu_3_wtd %>% format(digits = 5)` (`r sd_edu_3_wtd %>% format(digits = 4)`)

Some college mean (SD): `r mean_edu_4_wtd %>% format(digits = 5)` (`r sd_edu_4_wtd %>% format(digits = 5)`)

College graduate mean (SD): `r mean_edu_5_wtd %>% format(digits = 5)` (`r sd_edu_5_wtd %>% format(digits = 4)`)

Refused mean (SD): `r mean_edu_7_wtd %>% format(digits = 3)` (`r sd_edu_7_wtd %>% format(digits = 4)`) (1 obs)

Don't know mean (SD): `r mean_edu_9_wtd %>% format(digits = 3)` (`r sd_edu_9_wtd %>% format(digits = 3)`) (1 obs)

## Povery ratio
```{r pov, include=FALSE}
# Weighted
plot_pov_wtd <- qplot(income_pov_ratio, bld_tc, weight = weight_mec) +
  geom_smooth(formula = y ~ x, method = 'lm') +
  labs(x = 'income to poverty ratio',
       y = chol_label, title = 'Cholesterol by poverty ratio, weighted')
model_pov_wtd <- svyglm(bld_tc ~ income_pov_ratio, svy1)
model_pov_tbl_wtd <- model_pov_wtd %>% tidy(conf.int = T)
model_pov_tbl_wtd[2, 1] <- 'Income to poverty ratio'
model_pov_tbl_wtd$p.value <- format(model_pov_tbl_wtd$p.value, digits = 3)
model_pov_tbl_wtd <- model_pov_tbl_wtd %>% kable()
# Correlation
v_pov_wtd <- svyvar(~bld_tc + income_pov_ratio, svy1, na.rm = T)
c_pov_wtd <- cov2cor(as.matrix(v_pov_wtd))[1, 2] %>% format(digits = 4)
```

### Weighted
```{r pov2, echo=FALSE}
plot_pov_wtd
model_pov_tbl_wtd
```

Correlation: `r c_pov_wtd`